From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-08 Pi+/paper/finite.tex
Say horizontal and vertical categorification

% Recap of the previous section
In~\Cref{sec:ufin}, we established that paths in $\UFin$ are equivalent to families of loops on $\Fin[n]$ for every
$n:\Nat$, that is, automorphisms of finite sets of size $n$, with the loopspace encoding the automorphism group. This is
also known to be the finite symmetric group $\Sn[n]$. In the following sections, we will describe this group
syntactically.

>>>>

% Recap of the previous section
In~\Cref{sec:ufin}, we established that paths in $\UFin$ are equivalent to families of loops on $\Fin[n]$ for every
$n:\Nat$, that is, automorphisms of finite sets of size $n$, with the loopspace encoding the automorphism group.  This
is also known to be the finite symmetric group $\Sn[n]$, making $\UFin$ the \emph{horizontal categorification} of $\Sn$
for every $n$. In this section, we will describe this group syntactically.
